Flute and kink instabilities in a dynamically twisted flux tube with anisotropic plasma viscosity

### 2022-02-14 paper.tex
Soften statement on where we know the perturbation to grow

The location of the peak \rev{fluting growth rate $r_s$} matches
nearly exactly the location of the resonant surface where the observed perturbation grows
(Figure~\ref{fig:swi-4_pressure_13}) and an estimate of the linear growth rate
can be found by averaging $\gamma$ over $r$, giving a growth rate of $0.86$.

>>>>

The location of the peak \rev{fluting growth rate $r_s$} aligns well with the location of the resonant surface where the observed perturbation appears to grow
(Figure~\ref{fig:swi-4_pressure_13}) and an estimate of the linear growth rate
can be found by averaging $\gamma$ over $r$, giving a growth rate of $0.86$.
